---
title: "Projects"
output:
  html_document:
    toc: true
    toc_float: true
---

 

```{r, include=FALSE}
library(ggplot2)
library(dplyr)
library(readxl)
```

These are plots that are made to show the real life, publicly available, NCDC data for Cholera, Cerebrospinal Meningitis (CSM), Lassa Fever, Measles, Monkey Pox, and Yellow Fever. This was an assignment given to me at [The Know Place](https://theknowplace.github.io) where I learned the Fundamentals of R programming taught by [Ms.Chiomah Ezeomah](https://chiomahezeomah.github.io). I used R language to code the data from the NCDC into readable plots.

```{r, include=FALSE}
ncdc.data<-read_xlsx("C:/Users/AREETAM/OneDrive/Documents/R Language lessons/ncdc_2024.xlsx",sheet=1)
```

```{r, include=FALSE}
head(ncdc.data)
```


### Line Plot

This line plot shows which illnesses report more cases every week.As you can see from the plot, Measles has more reported cases than Lassa fever and Cholera. If you look from week 20 to week 40 you can see that Lassa fever cases begin to reduce and Cholera cases start to increase.
```{r, echo=FALSE, warning=FALSE}
ggplot(ncdc.data,aes(epid.week,cases,colour = disease))+
  geom_line(size=0.75)+
  scale_color_brewer(palette = "Set1", labels=c("Cholera","CS Meningitis","Lassa fever", "Measles","Mpox","Yellow fever"))+
  theme_bw()+
  xlab("Weeks")+ theme(axis.title.x = element_text(vjust = 0.5, size=12,face = "bold"))+
  ylab("No.of Cases")+theme(axis.title.y = element_text(hjust = 0.5, size = 12, face = "bold"))+
  labs(title = "Plot of Reported Illness Per Week in Nigeria")+theme(plot.title = element_text(size = 16,hjust = 0.75,face = "bold"))+
  labs(color="Disease")+theme(legend.title = element_text(size=12,face = "bold",hjust = 0.5))+
  theme(legend.background = element_rect(color = "#F40D1D"))
```


### Box Plot


In this Box Plot it shows the median out of all the number of cases for one disease, it shows this by putting a  horizontal line where the median is for the total number of cases. An example is, the median of Measles is around 120, but the highest number of cases is 898 and the lowest is 0. These numbers are shown on the vertical line, the highest number is at the top while the lowest number is at the bottom of the line.

```{r, echo=FALSE, warning=FALSE}
ggplot(ncdc.data,aes(disease,cases,colour = disease))+
  geom_boxplot(size=0.45)+
  scale_color_brewer(palette = "Set1", labels=c("Cholera","CS Meningitis","Lassa fever", "Measles","Mpox","Yellow fever"))+
  theme_bw()+
  xlab("Disease")+ theme(axis.title.x = element_text(vjust = 0.5, size=12,face = "bold"))+
  ylab("No. of Cases")+theme(axis.title.y = element_text(hjust = 0.5, size = 12, face = "bold"))+
  labs(title = "Plot of Reported Illness Per Week in Nigeria")+theme(plot.title = element_text(size = 14,hjust = 0.5,face = "bold"))+
  labs(color="Disease")+theme(legend.title = element_text(size=10,face = "bold",hjust = 0.5))+
  theme(legend.background = element_rect(color = "#8B131D"))+scale_x_discrete(labels=c("Cholera","CS Menigieties","Lassa fever", "Measles","Mpox","Yellow fever"))
```


### Bar Plot 

In this bar plot, the total number of cases per disease is represented. Measles is the highest while Lassa is second, and Cholera is third. In summary Measles has the highest reported cases while Mpox has the the lowest reported cases.
```{r, echo=FALSE, warning=FALSE}
ggplot(ncdc.data, aes(disease,cases,color=disease, fill = disease))+
 geom_bar(stat = "identity", fill="red", color = "red")+
  xlab("Disease") + theme(axis.title.x = element_text(vjust = 0.5,size = 12, face = "bold"))+
  ylab("No. of Cases") + theme(axis.title.y = element_text(hjust = 0.8, size = 12, face = "bold"))+
  labs(title = "Bar Plot of Reported Illness per Week in Nigeria")+ theme(plot.title = element_text(size = 14, hjust = 0.5, face = "bold"))+
  theme_bw()+scale_x_discrete(labels=c("Cholera","CS Menigieties","Lassa fever", "Measles","Mpox","Yellow fever"))
```
